We should have a page that uses pretentious Clement Greenberg-esque language to talk about "perspective" and "foreground" and "background" and "depth of field" and so forth. Most papers are pretty boring: a bird's eye view. But as Freeman Dyson notes, there are birds and frogs in research. And frogs like to get in the mud. And frogs like to croak about Budweiser. And frogs are in the background.

In the foreground of this page-long section, there is a giant can of Budweiser.

Publish untrue hit jobs on President's foes (it's not libelous if it's in ACM)
the puzzle section/mathematical recreations just solves computational problems for businesses -- "put ACM math recreations in the loop" to get your answer with no computational overhead and a one-month delay

E.g. suppose you are a major defense contractor Paytheon, and you've been asked to bid on a government contract with options (whose details are classified) in table A, and for each option you have a guess of the probability (table B) that the government will actually go for that option. Your estimated costs are in table C. You know your bid will be evaluated based on the overall ensemble of prices in your bid -- a weighted sum of the options with unknown weights. Can assign prices in such a way that you jack up the price on the things you expect the government to buy and lower the price on the things you expect the government not to buy -- with the constraint that you wish to avoid dramatic price swings that can sway the government's decision -- in such a way as to maximize expected profits? Can you also concoct some phony scholarship to rationalize your illegal prices, with a deck of briefing slides and a ten-page white paper?

guide to april fools day pranks that won't embarrass your teen
old faithful superior accuracy as computer clock
old glory which thought was old faithful but retain for it superior

Academics can get around laws through fair use
good: HEY KIDS learn how JOE CAMEL targeted kids and got them to see how COOL smoking can be
bad (challenges authority): number theorists wrote a paper on the number-theoretic properties of "the nuclear code" numbers

ACM pep rallies: a single academic article will be fired from a cannon but invariably so many people fight over it it just shreds to pieces

ACM vending machines, human-staffed, particularly cruel topple people who stick hand in (or maybe joke about papers being can-shaped so if you try to steal one, you get stuck in the vending machine unless you decide to let go of the can. The Virginia state legislature has approved a measure that would allow tobacco companies to generously contribute to the ACM and the advancement of science (withheld from the wages of 14-year-old tobacco pickers), by furnishing vending machines that sell cigarette packs with snippets of technical papers on them, over the space on the pack where the Surgeon's General Warning used to go. Each vending machine would be affiliated with a particular ACM journal.