* one of the links referenced is a terrifying URL that ends in .exe

* Featurette: Does Commercialism Chill Scientific Inquiry (sponsored by Chill's restaurant): Take a look at science -- people valorize metrics, hack p-values, hype results for media coverage and access to scarce research funds, try to boot the ego. Paul Erd\"os may have been right about math but he's wrong about science. Science is a machine for converting sacred principles (openness) and good-to-the-last-drop Maxwell House coffee ("We gave you a Haggadah. It's the least you could do.") into profane, Taylorizable metrics (openness scores). Science is a rat race already. The introduction of incentives for commercial relevance need not constrain the liberty of researchers. Is the pursuit of science that is flattering to the scientist any different than the pursuit of science flattering to the all-new 2017 Jep Liberty? Discuss the latest research about the miracle superfood bacon-wrapped rib nachos at your neighborhood Chill's today!  

* Don't think that the easy-to-grasp numbers are necessarily more widely grasped. The ACM children's program, \emph{Shareware Street}, in a disgusting commercial display, infamously allows the numbers with the deepest pockets to sponsor its programming. Consequently, some brands may choose to purchase numbers more abstruse (i.e., admitting no obvious simple English formulation) that they may have money the more with which to bribe \emph{Shareware Street} producers. 

* Keep in mind, while sponsors purchase naming rights based on a \emph{description} of a number or set, they are in fact purchasing the number itself. If a speculator purchases, based on a description, a number that turns out not to exist, the speculator is left with nothing, whereas the purchaser of the paradox---the giving a name to a non-existent thing---involving the description, would remain a sponsor of the paradox if it is indeed a valid paradox. If someone purchases, based on description, a number that is already sponsored by another entity, she owes that entity 50 push-ups.

 

Oubliez le zoo Franklin Park, visitez le parc d'attractions Terrain de ACM (anciennement Euro Disney)
Découvrez le nouveau terrain inspiré par le film qui a arraché le coeur des critiques de films et les a rendu méchants, *It's a La, La, La Land*
Osez entrer dans la salle des Georges Will (Milos) 

ACM goofs gotchas and glitches:
Reader Jess of Muscle Shoals, AL, sent in this photo. It's a public park but there are no ads! Oops!

ACM: a religion centered on collecting rent -- the purest, most holy & efficient interaction between quasi-consenting humans is that of landowner and tenant/peasant; assigning rights to absentee owner & allowing him to charge those who use space on this planet is a form of spiritual communion with the planet. It's sacred. We can't do that all the time in our post-agrarian society, so we work with absentee owners of intellectual property, like designs, technological methods, mathematics, language. The devil Nekhlyudov is a fallen idol and wants to get in the way of our religion. Think of the Alabama Secretary of State (was it?) who said you can't appreciate voting if it's easy, you can't respect voting -- this is how we respect the math commons. It's open access. But you have to pay rent to use it. Paying the license fee, like paying the poll tax, affirms one's love of this sacred act of paying rents. Open access with strict end-user license agreements is the fundament of an open society.

Ride the Möbius transformation at ACM Land: "I survived -- and I all got were these stretch marks."

In the beginning G-d, created intellectual property (Genesis FBI Warning) 

spin associate, citizen builder of the Leviathan, seeking on her or his own liberation from
Adorno said that ?Marx wanted to turn to the world into a giant workhouse?

First (here we enter narrative importance but not narrative time, as part of a best practice to limit time-travel paradoxes), we wish to show... 

ACM chewing tobacco.

Big Cat wants you to think the parasite isn't targeted at humans
They're teaching our kids to hate Big Red Dog
Evolution has no direction but money talks (and it swears)
Pay the parasites to hijack your brain to enjoy ACM cola
Prior work: Lancet river fluke
ACM frogs (A C M instead of Bud-Wei-Ser)
ACM Sells Parasites

The ACM pays birds to trace out the nams of ACM products and fly in formations that constellate into the logos of ACM brands. The ACM pays people to give birth to th mascot of ACM Burger Town (cf., *Rosemary's Baby*) -- namely, the combined hamburger thief/king dressed in a prisoner's outfit and wearing a crown, an illegitimate ruler who exercises power by demanding the *dizaine* tax payment, i.e. ten burgers per day. The president of the ACM was bribed with "alien bucks" by ostensible aliens who didn't even promise to not murder him or other members of the human race in exchange for tender that was neither legal nor wanted on a planet whose governments' taxes aren't violently collected in that currency.

My favorite birds: the red breasted nuthatch, the old money sparrow, the pretentiously named grosbeak. I'm on the red-breasted-nuthatch diet. 


Guys, I finally figured out why Clear Channel keeps putting up those THIS YEAR, GIVE HER AN STD billboards you see everywhere.

You know how the juvenile lancet liver fluke hijacks infected ants' brains and makes them cling to the tops of blades of grass each night till a cow eats the blade of grass, along with the lancet liver flukes inside?* Well, something very similar is happening in the brains of Clear Channel ad execs. What's even weirder is that different parasites hijack the brains of drivers to make them read the billboard as THIS YEAR, GIVE HER UNTREATED WATER. #stanleythoughts #acm

*Yep. https://en.wikipedia.org/wiki/Dicrocoelium_dendriticum#Life_cycle
>Dicrocoelium dendriticum spends its adult life inside the liver of its host. After mating, the eggs are excreted in the feces.
ACM: scientists who work on reproducing class privilege perfectly while calling it meritocratic (meritocracy is kleptocracy with good PR) -- the so-called Jared Kushner problem
PR so good one can speak the plain truth w/o fear of causing ill discipline in the factories because nobody will internalize the truth. 

ACM: computational recreations greetings puzzlers, Paytheon
winners get a certificate of thanks (unfortunately, due to our high volume of solitaire matches, we?re unable to personalize these)
winner gets alvin & chipmunks movie ticket (offer applies only to the movie Chipwrecked, if you can persuade some theater to play it, winner gets two tickets if and only if the total cost comes out to exactly $10.01 with tax.

ACM: dancing airman online auto insurance ad

ACM: As researchers {female first names} proved in {the reference: name of the first author shows off baby bump at computing conference}, P != NP.

ACM Show the people, show not tell. Chyron/scrolling news ticker in paper but for ads ? use the tool that is used to draw eyeballs away from ads against itself ? to advertise!

ACM Any resemblance to living information is purely coincidental or due to the permanence of human behavior or because I spilled coffee on the manuscript making it heteroglossic
art criticism about depth of field and how the page really is 3D a canvas is physical with a big Bud Light can in front, Bud frogs behind


ACM: computational recreations greetings puzzlers, Paytheon
winners get a certificate of thanks (unfortunately, due to our high volume of solitaire matches, we?re unable to personalize these)
winner gets alvin & chipmunks movie ticket (offer applies only to the movie Chipwrecked, if you can persuade some theater to play it, winner gets two tickets if and only if the total cost comes out to exactly $10.01 with tax.

ACM: dancing airman online auto insurance ad

keep in check?in the asteroidal subdivision did ACM a tract of stately space
pleasure domes decree, commutes vary from 2-24 months. albedo may vary to prevent
impact with earth. the spread of democratic vulgarity, a shapeless jelly of human stuff.
?easier than convincing home owning NIMBYs to allow the supply of affordable housing here on earth to increase? since the masses hate the masses and since normcore is in among the elite (i?ve read) why don?t i decide to hate the masses to be more like the masses, to distinguish myself. i was practicing emancipatory social relations with my liver. milo wore a shirt that says STOP BEING POOR. i want one that says STOP BEING MILO. people = shit = shit. (people = shit) = shit. professor of angles. ACM ads: FBI and chili bowl: ?a DC institution? (has a no hunting sign) IRS ?money-back guarantee? (same generic look, no taste) homogeneity architects (has a no hunting sign): ?we build boring homogeneous cities so hollywood can cheaply recreate them.? the accountant couldn?t account for his feelings. the bomber couldn?t bomb away the feelings of potency.

The ACM?s lectures are sponsored much the way megachurches were paid to work in the ?Jesus: the original Superman? angle before the Superman movie.

I heard on the bus that there was an Air Force project that looked into ionospheric modification ? heating the ionosphere to make communication more feasible. I heard on the garbage barge that Serak the Preparer ? author of how to cook (for ((for)ty)) humans, with space dust and Milpool ? found out the gene that causes the birth defect of being a lumper i.e. one who loads and unloads trucks, usually with a forklift. He found it through abductive reasoning ? which is what the ACM will use in its articles once the greys take over. But don?t mind me. I?m typing AT commands at my modem and watching elevator TV (which is somehow legal even though you can?t watch TV while driving). I?m taking the elevator down to my neighborhood Paul Ryan work dungeon. Remember when poor kids got healthcare even if their parents didn?t walk 20 miles to the work dungeon and work for two days straight and walk back to sleep for ten hours and say hi to the kids and go back to the ACM work dungeon. I keep old food in the fridge not because I am afraid of throwing it away but rather because I?m waiting for it to get better. People don?t understand STATISTICAL mechanics. There is a chance many of the world?s caviar molecules will accumulate there and the bacterial toxins will go bug someone else.

ACM?s ASTEROIDAL SUBDIVISION: DON?T CALL US, WE?LL DRAFT YOU
when numbers are branded, Sesame Street will be a more relevant experience for young consumers.

-- But isn't the ACM just alienating the workers it puts in the work dungeons?
-- Nah, man -- it's totally cool. *Marx himself* came up with the theory of alienation.

The ACM also supports the reification of numbers. Not only does it assert that every number for which one can come up with a name exists as a brandable number (even paradoxical numbers such as the JC Penny "the smallest positive integer that cannot be uniquely described in fewer than sixteen English words" and Perk Boys's "the Presidents' Day number" and Althusser's "human social relations number"), but that it also exists in the physical world. These numbers can be found on ACM's location-based augmented reality game, "The Frogs Are All Gay. Go Look for and Catch Numbers or Something, Kids."


a form of peer review: post your paper on a telephone poll, with a large margin at the bottom of the paper, so that each sheet is a tear-off flyer, and the tear-off strips don't point you to a Web site but rather can be slipped into a nearby suggestion box ACM


autoplay Bob Dylan he will always have new track to advertise b/c whenever he dies the ACM will produce new BD songs with the first Nobel-winning algorithm
IEEE is too busy trying to convince Teamsters to become electrical engineers to produce real science, integrative science
set theory: law of the excluded middle, dialethism, intuitionism, Grow the engagements, grow the brand.

Giving customers the opportunity to engage and interact with a product or service is the most powerful way to win brand loyalty. AgencyEA strategically engages consumers in their natural environments to establish deep brand connections. From mobile tours and product launches to local activations and product sampling, our B-to-C engagement solutions communicate brand attributes at every touch point.

Developed to strategically function as part of an integrated marketing plan, these initiatives help increase brand awareness, generate press exposure, drive traffic and sales, and create consumer loyalty. EA?s expertise in experiential marketing, combined with in-house production, digital and creative capabilities, enables us to deliver consumer programs that build relationships, influence behavior and motivate action.
Materials section: look at all this shit! 6 cadillacs 5 fords, three mercuries a T-bird
citizens will be monitored for quality assurance 
(john lennon had a climate-controlled room for his fur coats when he wrote "imagine?"


The ACM never forgets to cite the W3C, the Gorka Briefing, backward rock music

The ACM: "We don't inspect proofs very closely"

I spark action potentials with ACM. It bypasses sense organs and sparks 'em directly. My tears tend to arise with certain aspects of film scores in movies, but that doesn't mean ACM isn't sparking my action potentials. 

